### 2023-08-17 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny3

When a vesicle is tank-treading near a solid wall, the flow in the thin
layer of fluid includes both a linear profile and a Poiseuille
profile~\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}.
The magnitude of the Poiseuille profile is determined by the pressure
gradient between the vesicle and the solid wall, while the linear
profile is determined by the tangential velocity of the vesicle relative
to the solid wall. Using the definition of the lubrication layer
outlined in Section~\ref{sec:LL}, we consider the flow profile inside
this lubrication layer in Figure~\ref{fig:BLvelocities}. We observe that
the Poiseuille coefficient (quadratic term) can be either positive or
negative, meaning that the pressure gradient in the streamwise direction
in the lubrication layer switches signs. The Poiseuille coefficient is
related to the lateral gradient of the tangential traction,
$\mathbf{F}_\tt$, on the vesicle membrane~\cite{Oron1997_RMP,
Young2014_JFM}
\begin{align}
  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u}.
\end{align}
Here,
\begin{align}
  \frac{\delta E^m}{\delta u} = \frac{a}{\epsilon} 
    (f'(u) - \epsilon^2 u_{ss}) + \frac{b'(u)}{2} \kappa^2
\end{align}
is the derivative of the membrane energy with respect to the lipid
concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
single-component case, the tangential traction is $\mathbf{F}_\tt =
-\sigma_s$ which is the Marangoni stress.  For a single-component vesicle, the streamwise gradient 
of the Marangoni stress determines the sign of the Poiseuille coefficient in Figure~\ref{fig:BLvelocities}(a).
For a multicomponent vesicle, the Poiseuille coefficient can also change sign around the boundary 
between two lipid domains, where the membrane energy changes sharply between lipid species. This implies that, by visualizing the flow
in the lubrication layer, it is possible to identify the location of boundaries between lipid domains as shown in Figure~\ref{fig:BLvelocities}(b).

>>>>

When a vesicle is tank-treading near a solid wall, the flow in the thin
layer of fluid includes both a linear profile and a Poiseuille
profile~\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}.
The magnitude of the Poiseuille profile is determined by the pressure
gradient between the vesicle and the solid wall, while the linear
profile is determined by the tangential velocity of the vesicle relative
to the solid wall. Using the definition of the lubrication layer
outlined in Section~\ref{sec:LL}, we consider the flow profile inside
this lubrication layer in Figure~\ref{fig:BLvelocities}. We observe that
the Poiseuille coefficient (quadratic term) can be either positive or
negative, meaning that the pressure gradient in the streamwise direction
in the lubrication layer switches signs. The Poiseuille coefficient is
related to the lateral gradient of the tangential traction,
$\mathbf{F}_\tt$, on the vesicle membrane~\cite{Oron1997_RMP,
Young2014_JFM}
\begin{align}
  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u}.
\end{align}
Here,
\begin{align}
  \frac{\delta E^m}{\delta u} = \frac{a}{\epsilon} 
    (f'(u) - \epsilon^2 u_{ss}) + \frac{b'(u)}{2} \kappa^2
\end{align}
is the derivative of the membrane energy with respect to the lipid
concentration~\cite{soh-tse-li-voi-low2010}. For a single-component vesicle,
the tangential traction is $\mathbf{F}_\tt =-\sigma_s$ (the Marangoni stress), and  the streamwise gradient 
of the Marangoni stress determines the sign of the Poiseuille coefficient in Figure~\ref{fig:BLvelocities}(a).
For a multicomponent vesicle, the Poiseuille coefficient can also change sign around the boundary 
between two lipid domains, where the membrane energy changes sharply between lipid species. 
This correlation between the location of the boundary between lipid domains and the fluid velocity profile in the lubrication layer
implies that, by visualizing the flow
in the lubrication layer and identifying locations where the nonlinear shear flow profile is convex, 
it is possible to identify the location of boundaries between lipid domains as shown in Figure~\ref{fig:BLvelocities}(b).
